\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-20 coq-example.tex
Save. Third Example.

\newpage\EDJ{Please delete this newpage command later}
We provide two examples here for illustration and evaluation of our Coq plugin.

@@

>>>>

\newpage\EDJ{Please delete this newpage command later}
We provide three examples here for illustration and evaluation of our Coq plugin.

@@

\subsection{An Extensible Decision Procedure for Parsing}
The third example is a decision procedure for parsing. The basic idea is that we can use Cop's Inductive Facility to encode CFG rules. Then extensible inductive family corresponds to extensible CFG rules. For example, indexed type \mintinline{Coq}{is_prog : strs → Type} indicate a token list is a syntacitcally well-formed program.

To prove \mintinline{Coq}{forall s, (is_prog s) + (is_prog s -> False)}, we use strong induction on the length and the non-trivial part is at the inductive step, i.e. we need to show \mintinline{Coq}{(forall e, len e < len s -> (is_prog e) + (is_prog e -> False)) -> (is_prog s) + (is_prog s -> False)}.

Then we provide an overridable predicate \mintinline{Coq}{alg_is_prog : strs -> Type}, decidable provided the inductive hypothesis and sound \& complete w.r.t. to the specification \mintinline{Coq}{alg_is_prog e  <-> is_prog e}. We require extension to take care of the soundness \& completeness and the conditional decidablity.

Among them, completeness \mintinline{Coq}{is_prog e -> alg_is_prog e} is the most challenging part. This is proved by recursion on the predicate "is_prog e", but most of the handler on "is_prog" will not be reused because \mintinline{Coq}{alg_is_prog e} is overriden during inheritance. Unlike completeness, other parts of the construction, including soundness and and conditional decidability can be reused easily.

### 2022-10-20 metatheory-condensed.tex
Save. Third Example.

Adding new types into signature \ruleref{Sig Add} requires a \textit{sealing judgement} $\goodSeal{\Gamma}{f}{\sigma}{A}$, which is an alias of a term judgement. Intuitively, sealing can abstract any given type by indicating a morphism to the interface. Sealing is a convenient device when programming using meta-theory, \textit{to indicate whether each field is overridable, non-overridable (thus definitionally exposed) or extensible}. For example, if a field is overridable, we abstract that to its type; if a field has exposed its definition, we abstract it into the singleton type containing it instead.

@@

% Inhertance judgement
In the plugin implementation, "Family"s are second class objects like Coq's "Module". What's more, a "Family" (with or without "extends" clause) can be considered as a standalone piece of code trying to \textit{inherit} an existent (but maybe empty) family. Thus we model them using \textit{inheritance judgement} $\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}$ instead of considering them as first class terms. The only way to use $h$ is by \ruleref{Inh} and transforming a linkage of signature $\sigma_1$ to another linkage of $\sigma_2$.

Inheritance judgement can be further enriched with inheriting operation, overriding operation, extending operation and etc. These operations correspond to inherit, override and extend command inside "Family" in our plugin implementation.

>>>>

Adding new types into signature \ruleref{Sig Add} requires a \textit{sealing judgement} $\goodSeal{\Gamma}{f}{\sigma}{A}$, which is an alias of a term judgement. Intuitively, when programming using meta-theory, sealing is a convenient device \textit{to indicate whether each field is overridable(extensible) or non-overridable (thus definitionally exposed)}. For example, if a field is overridable, we abstract that to its type; if a field has exposed its definition, we abstract it into the singleton type containing it instead.  Sealing $\goodSeal{\Gamma}{f}{\sigma}{A}$ is useful when the surrounding interface is $\sigma$ and we want to construct the new field based on $A$.

@@

% Inhertance judgement
In the plugin implementation, "Family"s are second class objects like Coq's "Module". What's more, a "Family" (with or without "extends" clause) can be considered as a standalone piece of code trying to \textit{inherit} an existent (but maybe empty) family. Thus we model them using \textit{inheritance judgement} $\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}$ instead of considering them as first class terms. The only way to use $h$ is by \ruleref{Inh} and transforming a linkage of signature $\sigma_1$ to another linkage of $\sigma_2$. Inheritance judgement can be inductively constructed via inheriting operations, overriding operations, extending operations and etc, corresponding to "Inherit", "Override" and "Extend" command  in our plugin implementation.
